Multi-view 3D Aerosol Distribution Recovery

### 2013-07-30 article.tex
Cleanup of redundnat references

In remote sensing~\cite{Mishchenko2007}, imaging through air is associated with
{\em atmospheric correction}, based on {\em aerosol retrieval}. In
this discipline, the atmosphere is often assumed to be plane-parallel,
using one-dimensional vertical RT. Consequently state-of-the-art
aerosol retrieval is done in distinct large lateral
blocks~\cite{Martonchikc} with limited height
resolution~\cite{kalashnikova}. We, however, seek 3D
recovery. Atmospheric correction is related to
dehazing~\cite{Namer2009,Zhu2013}. In this paper, however, the medium
itself, at all relevant altitudes is the object of interest.

We rely on sky imaging from multiple directions and locations. Such
projection is similar to tomography in other scientific
domains~\cite{Bluestone2001}. However, the situation here is distinct. Most
tomography setups have a controlled and/or multidirectional radiation
source~\cite{Boas2001,messer}. In contrast, our source is the
uncontrolled, unidirectional Sun. Moreover, typical tomography relies
on a linear model~\cite{gregson}: the pixel value is a linear
combination of components along a line of sight (LOS), or a
multiplicative combination (linearized by a logarithm). Linear
tomography can detect
gases~\cite{Kazahaya2008,Price2001,Cosofret2009,wright}, which absorb
UV or IR radiation. However, aerosol attenuation of visible light is
typically dominated by {\em scattering}, rather than absorption. Since
the radiation source is single and fixed in space and time, we cannot
rely on direct illumination for tomographic recovery of attenuation
fields~\cite{Aviles2011}. We may only use sunlight scattered into the
LOS. The model is {\em nonlinear, yet tractable}. We model passive
optical tomographic imaging of 3D atmospheric scatterer distributions
in cloudless conditions. Then, we solve this tomography problem, to
recover the distribution. Recovery is formulated as an optimization
that minimizes a cost function. We derive the gradient of this cost
function, to enable efficient optimization.

>>>>

In remote sensing~\cite{Mishchenko2007}, imaging through air is associated with
{\em atmospheric correction}, based on {\em aerosol retrieval}. In
this discipline, the atmosphere is often assumed to be plane-parallel,
using one-dimensional vertical RT. Consequently state-of-the-art
aerosol retrieval is done in distinct large lateral
blocks~\cite{Martonchikc} with limited height
resolution~\cite{kalashnikova}. We, however, seek 3D
recovery. Atmospheric correction is related to
dehazing~\cite{Namer2009}. In this paper, however, the medium
itself, at all relevant altitudes is the object of interest.

We rely on sky imaging from multiple directions and locations. Such
projection is similar to tomography in other scientific
domains~\cite{Bluestone2001}. However, the situation here is distinct. Most
tomography setups have a controlled and/or multidirectional radiation
source~\cite{Bluestone2001,messer}. In contrast, our source is the
uncontrolled, unidirectional Sun. Moreover, typical tomography relies
on a linear model~\cite{gregson}: the pixel value is a linear
combination of components along a line of sight (LOS), or a
multiplicative combination (linearized by a logarithm). Linear
tomography can detect
gases~\cite{Cosofret2009}, which absorb
UV or IR radiation. However, aerosol attenuation of visible light is
typically dominated by {\em scattering}, rather than absorption. Since
the radiation source is single and fixed in space and time, we cannot
rely on direct illumination for tomographic recovery of attenuation
fields~\cite{Aviles2011}. We may only use sunlight scattered into the
LOS. The model is {\em nonlinear, yet tractable}. We model passive
optical tomographic imaging of 3D atmospheric scatterer distributions
in cloudless conditions. Then, we solve this tomography problem, to
recover the distribution. Recovery is formulated as an optimization
that minimizes a cost function. We derive the gradient of this cost
function, to enable efficient optimization.
